---
title: "Project Details"
params:
  output1: NA
  output2: NA
  output3: NA
  output4: NA
  output5: NA
  output6: NA
  output7: NA
  output8: NA
  output9: NA
  output10: NA
  output11: NA
  output_jur: NA
  output_apn: NA
  output_mit_names: NA
 # output12: NA
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE, comment=NA)
library(formattable)
library(tidyverse)
library(scales)
```

The tool provides initial screening for all project types and more detailed analysis for residential, tourist accommodation unit, and public service projects.  All non-screened commercial, recreation, and other projects will need to complete a more detailed transportation analysis. For detailed information on the PIA  framework, tool usage, and calculations see the User Guidelines.

### Date Submitted

```{r, echo=F}
cat(date())
```

### Project Name

```{r, echo=F}
cat(params$output6, "\n")
```

### Type

```{r, echo=F}
cat(params$output7, "\n")
```

### Size

```{r, echo=F}
cat(params$output8, "\n")
```

### Did this project screen?

```{r, echo=F}
cat(params$output1, "\n")
```

### Project VMT

```{r, echo=F}
cat(params$output2, "\n")
```

### Standard of Significance VMT

```{r, echo=F}
cat(params$output3, "\n")
```


### VMT Mitigation Needed

```{r, echo=F}
cat(params$output4, "\n")
```


### Mobility Fee 

```{r, echo=F}
cat(params$output5, "\n")
```

### Located in Town/Regional Center

```{r, echo=F}
cat(params$output10)
```

### Located in Bonus Unit Eligible Area

```{r, echo=F}
cat(params$output11)
```

### Jurisdiction

```{r, echo=F}
cat(params$output_jur)
```

### Parcel Number (APN)

```{r, echo=F}
cat(params$output_apn)
```

### Mitigation Categories 

```{r, echo=F}
cat(params$output_mit_names)
```

### Mitigations Values

```{r, echo=F}
cat(params$output9)
```

